---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(MASS)
library(ggplot2)
library(plotly)
library(dplyr)
library(reshape2)
library(googlesheets)
```

## Downloading data 

We can begin by downloading data from the Google Drive responses, using the googlesheets plugin. The gs_ls function prompts us to authenticate with Google. The spreadsheet is then downloaded based on URL, and then we rename column headings and add an ID.

```{r download}
gs_ls()
responses<-gs_url("https://docs.google.com/spreadsheets/d/1E31U5SN7_FpHHlKsuPR02f0KIVSyWgLKeXho_lzGCzk/edit?usp=sharing")
responses_read<-gs_read(responses)
names(responses_read)<-c("Time","Pic1","Pic2","Pic3","Pic4","Pic5")
responses_read<-responses_read[,-1]
```

##Calculating co-occurances

Using the outer and vectorize functions, we can count the coccurances of each picture in the responses.

```{r calculate}
response.matrix<-outer(responses_read, responses_read, Vectorize(function(x, y) sum(x == y)))

#Create fit from sample data
item.dist<-dist(response.matrix)
fit<-isoMDS(item.dist,k=2)
fit

# plot solution 
x <- fit$points[,1]
y <- fit$points[,2]
plot(x, y)
text(x, y, labels = row.names(response.matrix), cex=.7)

#kmeans
dist.sample<-data.frame(cbind(x,y))
cluster.sample<-kmeans(dist.sample,2)
cluster.sample$cluster <- as.factor(cluster.sample$cluster)
plot<-ggplot(dist.sample, aes(x, y, color = cluster.sample$cluster)) + geom_point(size=10)
ggplotly(plot)

#hierarchical cluster
mds.dist<-dist(dist.sample)
hc<-hclust(mds.dist) 
plot(hc)
groups<-cutree(hc,k=8)

#Print HCA clusters (function from Practical Data Science in R)
print_clusters<-function(labels,k) {
  for(i in 1:k) {
    print(paste("cluster",i))
    print(SampleData1[labels==i,c("Type","Score")])
  }
}
print_clusters(groups,8)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
